**The status of the microbial census: an update**

### 2016-01-07 doc/notebook/Bacterial_data_acquisition.Rmd
Update processing status
Fix pre-cluster diffs

mothur "#set.dir(input=data/mothur, output=data/mothur);
        filter.seqs(fasta=all_bacteria.align, vertical=T, trump=., processors=8);
        unique.seqs();
        pre.cluster(fasta=current, name=current, diffs=10);"

@@

```{r cluster_data, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur, seed=1);
        cluster.split(fasta=all_bacteria.filter.unique.precluster.fasta, name=all_bacteria.filter.unique.precluster.names, taxonomy=all_bacteria.pick.taxonomy, taxlevel=2, classic=T, processors=8)"
```

>>>>

mothur "#set.dir(input=data/mothur, output=data/mothur);
        filter.seqs(fasta=all_bacteria.align, vertical=T, trump=., processors=8);
        unique.seqs();
        pre.cluster(fasta=current, name=current, diffs=12);"

@@

```{r cluster_data, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur, seed=1);
	cluster.split(fasta=all_bacteria.filter.unique.precluster.fasta, name=all_bacteria.filter.unique.precluster.names, taxonomy=all_bacteria.pick.taxonomy, splitmethod=classify, classic=T, taxlevel=2, cluster=F, processors=12)
	cluster.split(file=all_bacteria.filter.unique.precluster.file, processors=8, classic=TRUE)"
```

XXXXXXXXXX
